Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-04 methods_paper/fabl-paper.tex
fix figure and ask bk some questions.

\section{Simulation Studies}
\label{sec:simulations}

@@

	{\centering

		\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot} 
	}

	\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from Sadinle 2017. For each level of overlap and each level of error, we have 100 paired sets of 500 records.}\label{fig:sadinle_simulation}

\end{figure}

>>>>

\section{Simulation Studies}
\label{sec:simulations}
In this section, we consider a simulation study, nearly identical to that in \cite{sadinle2017}. \textcolor{red}{Brian: can you explain how it's the same versus different than what it is given in Sadinle as this would be the most helpful. Do you utilize Mauricio's exact files and approach and then do something else? If so, I would state this for clarity.}

\textcolor{red}{If you look in Sadinle (2017), did you use Table 2 or something else? Can you construct something similar to Figure 3 and Figure 4 as it's likely a reviewer will look at this paper and ask why you didn't do this exact comparison.}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot} 
\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from Sadinle 2017. For each level of overlap and each level of error, we have 100 paired sets of 500 records.}
\label{fig:sadinle_simulation}
\end{center}
\end{figure}

%
%\begin{figure}[ht]
%	
%	{\centering 
%		
%		\includegraphics[width=0.6\textwidth]{../notes/figures/sadinle_sim_plot} 
%	}
%	
%	\caption{Posterior means and credible intervals for accuracy metrics under the replication of simulation study from Sadinle 2017. For each level of overlap and each level of error, we have 100 paired sets of 500 records.}\label{fig:sadinle_simulation}
%	
%\end{figure}
